Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-11-01 ms.tex
using the profile line fit as a way to estimate flux

>>>>

\begin{figure*}
\gridline{
\fig{ratio_for_AZLab06_Baseline_487.pdf}{0.49\textwidth}{Ratio of the best fit line intercepts of 487 and 489}
\fig{allan_variance_for_AZLab06_Baseline_487_intercepts}{0.49\textwidth}{Allan variance of the ratio line series}
}
\caption{We can take the line intercept from Figure \ref{fig:illumGradientChangeOverTime} to calculate the flux.
This averages like $\sqrt{N}$ statistics.
}\label{fig:illumGradientChangeOverTime}
\end{figure*}
